Ethereum: Un Registro Generico delle Transazioni Sicuro e Decentralizzato \\ {\smaller \textbf{Final Draft - UNDER REVIEW}}

### 2016-02-01 Paper.tex
Update Paper.tex

In generale, l'Ether impiegato per acquistare il gas che non è rimborsabile è consegnato al \textit{beneficiary} indirizzo, the address of an account typically under the control of the miner. Transactors are free to specify any \textbf{gasPrice} that they wish, however miners are free to ignore transactions as they choose. A higher gas price on a transaction will therefore cost the sender more in terms of Ether and deliver a greater value to the miner and thus will more likely be selected for inclusion by more miners. Miners, in general, will choose to advertise the minimum gas price for which they will execute transactions and transactors will be free to canvas these prices in determining what gas price to offer. Since there will be a (weighted) distribution of minimum acceptable gas prices, transactors will necessarily have a trade-off to make between lowering the gas price and maximising the chance that their transaction will be mined in a timely manner.

>>>>

In generale, l'Ether impiegato per acquistare il gas che non è rimborsabile è consegnato al \textit{beneficiary} dell'indirizzo, che è tipicamente sotto il controllo del miner. Coloro che effettuano le transazioni sono liberi di specificare qualsiasi are free to specify any \textbf{gasPrice} che desiderano, tuttavia i miner sono liberi di ignorare le transazioni da loro scelte. Un prezzo più alto del prezzo del gas per una transazione dunque costerà di più al mittente in termini di Ether e consegnerà un valore più grande al miner e quindi avrà più possibilità di essere selezionato al fine di essere incluso da più miner. In generale, i Miner will choose to advertise the minimum gas price for which they will execute transactions and transactors will be free to canvas these prices in determining what gas price to offer. Since there will be a (weighted) distribution of minimum acceptable gas prices, transactors will necessarily have a trade-off to make between lowering the gas price and maximising the chance that their transaction will be mined in a timely manner.
